TacticToe: Learning the Game of Tactics

### 2018-02-15 tactictoe_jv.tex
updating tactictoe results

The MCTS evaluation, despite relying on the largest amount of collected data,
does not provide a significant improvement over a strategy relying on no
evaluation. One one hand, our predictor learning abilities is
limited. On the other hand, the evaluation function was designed to estimate
the provability of a goal. A more accurate evaluation could be based on an
estimation of the length of the proof required to close a goal.

>>>>

The MCTS evaluation, despite relying on the largest amount of collected data,
does not provide a significant improvement over a strategy relying on no
evaluation. The minor improvement seen in the table is most likely due to some 
variability in our experiments.
The main reason is that our predictor learning abilities is
limited and we are using the provability of lists of goals for evaluation. A 
more accurate evaluation could be based on an estimation of the length of the 
proof required to close a list of goals.
